\chapter*{List of Publications}
\addcontentsline{toc}{chapter}{List of Publications}
\label{lop}
\fancyhead[LO]{\textsc{List of Publications}}
\fancyhead[RE]{\textsc{List of Publications}}
\fancyhead[RO]{\thepage}
\fancyhead[LE]{\thepage}

\subsection*{In press}
\begin{enumerate}
\item
Imhof,~A.;\ \ Megens,~M.;\ \ Engelberts,~J.~J.;\ \ de Lang,~D. T.~N.;\ \ Sprik,~R.;\ \ Vos,~W.~L.\ \ Spectroscopy of
Fluorescein (FITC) Dyed Colloidal Silica Spheres, \textit{J.~Phys.~Chem.~B} \textbf{1999,} \textsl{103,} 1408-1415.

\item
Budzelaar,~P. H.~M.;\ \ Engelberts,~J.~J.;\ \ van Lenthe,~J.~H.\ \ Trends in Cyclopentadienyl-Main-Group-Metal Bonding,
\textit{Organometallics} \textbf{2003,} \textsl{22,} 1562-1576.

\item
Havenith,~R. W.~A.;\ \ Engelberts,~J.~J.;\ \ Fowler,~P.~W.;\ \ Steiner,~E.;\ \ van Lenthe,~J.~H.;\ \ Lazzeretti,~P.
\ \ Localisation and Reversal of Paratropic Ring Currents in Molecules with Formal Anti-Aromatic Electron Counts,
\textit{Phys. Chem. Chem. Phys.} \textbf{2004,} \textsl{6,} 289-294.

\item
Soncini,~A.;\ \ Domene,~C.;\ \ Engelberts,~J.~J.;\ \ Fowler,~P.~W.;\ \ Rassat,~A.;\ \ {van Lenthe},~J.~H.;
\ \ Havenith,~R. W.~A.;\ \ Jenneskens,~L.~W. \ \ A Unified Orbital Model of Localised and Delocalised Currents in Monocycles, from Anulenes to Azabora-Heterocycles, \textit{Chem. Eur. J.} \textbf{2005,} \textsl{11,} 1257-1266.

\item
Engelberts,~J.~J.;\ \ Havenith,~R. W.~A.;\ \  van Lenthe,~J.~H.;\ \ Jenneskens,~L.~W.;\ \  Fowler,~P.~W.\ \ The Electronic Structure of Inorganic Benzenes: Valence Bond and Ring-Current Descriptions,
\textit{Inorg. Chem.} \textbf{2005,} \textsl{44,} 5266-5272.

\item
Havenith,~R. W.~A.;\ \ van Lenthe,~J.~H.;\ \ Jenneskens,~L.~W.;\ \ Engelberts,~J.~J.\ \ On the Interpretation of Valence Bond Wavefunctions, \textit{Faraday Discuss.} \textbf{2007,} \textsl{135,} 299-308.
\end{enumerate}

